\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

\emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}} \cite{W3C-ShEx-Primer-2014,W3C-ShEx-Definition-2014,Prud'hommeaux-2014,Boneva-2014} specifies a language whose syntax and semantics are similar to regular expressions. ShEx associate RDF graphs with labeled patterns called \emph{shapes} which are used to express formal constraints on the content of RDF graphs. \emph{Resource Shapes (ReSh)} \cite{W3C-ReSh-2014} defines its own vocabulary for specifying shapes of RDF resources. Ryman, Hors, and Speicher define \emph{shape} as a description of the set of triples a resource is expected to contain and as a description of the integrity constraints those triples are required to satisfy \cite{Ryman2013}.

>>>>

\emph{Shape Expressions (ShEx)} \cite{W3C-ShEx-Primer-2014,W3C-ShEx-Definition-2014,Prud'hommeaux-2014,Boneva-2014} specifies a language whose syntax and semantics are similar to regular expressions. ShEx associate RDF graphs with labeled patterns called \emph{shapes} which are used to express formal constraints on the content of RDF graphs. \emph{Resource Shapes (ReSh)} \cite{W3C-ReSh-2014} defines its own vocabulary for specifying shapes of RDF resources. Ryman, Hors, and Speicher define \emph{shape} as a description of the set of triples a resource is expected to contain and as a description of the integrity constraints those triples are required to satisfy \cite{Ryman2013}.
